\Title

### 2023-06-14 Grimaldi-etal-BiolCybernetics.tex
correc Miles: intro

\keywords{\Keywords}
%
\maketitle
%
\section{Introduction}
%%%-----------------------------------------------------------------
\label{sec:intro}
%
The human brain has the remarkable capacity to react efficiently at any given time while consuming a reasonable amount of energy, about tens of watts. This system is the result of millions of years of natural selection, and a striking difference with artificial neural networks is the representation that both use. Artificial convolutional neural networks (CNNs), for example, represent the flow of information from one layer to another as analog tensors, storing visual information densely across the visual topography, with different translation-invariant properties represented in different channels. CNNs have achieved state-of-the-art performance for some computer vision tasks, such as image recognition. These networks are also known to mimic many properties of biological systems, such that each can be assigned a ``brain score''~\citep{schrimpf_brain-score_2020}, but this score does not take into account inference speed or energy consumption. In fact, they do not take advantage of the dynamics inherent in the way we perceive our natural environment. In the vast majority of biological neural networks, on the other hand, information is represented as \emph{spikes}, prototypical all-or-nothing events whose only parameters are their timing and the address of the neuron that fired the spike~\citep{paugam-moisy_computing_2012}. Spiking neural networks (SNNs), known as the third generation of artificial neural networks, incorporate this temporal dimension into the way they perform their computations. They are of interest to computational neuroscience because they provide a better model of the biological neuron. One is the SpikeNet algorithm, which takes a purely temporal approach by encoding information using one spike per neuron~\citep{delorme_spikenet_1999}. Another type of SNN that uses the exact timing of spikes tries to determine the structure of the network to minimize a cost function, as implemented in the SpikeProp algorithm~\citep{bohte_error-backpropagation_2002}. This was recently extended using the surrogate gradient method which is now widely used in attempts to transfer the performance of CNNs to SNNs~\citep{zenke_remarkable_2021}. However, the performance of SNNs still lags behind that of networks using an analog, firing rate-based representation. The question of the advantage of using spikes in machine learning and computer vision remains open.

>>>>

\keywords{\Keywords}
%
\maketitle
%
\section{Introduction}
%%%-----------------------------------------------------------------
\label{sec:intro}
%
The human brain has the remarkable capacity to react efficiently at any given time while consuming a reasonable amount of energy, in the order of tens of watts. This system is the result of millions of years of natural selection, and a striking difference with artificial neural networks is the representation that both use. For instance, the convolutional neural networks (CNNs) which are used for processing images represent the flow of information from one layer to another using tensors of floats, storing visual information densely across the visual topography, with different translation-invariant properties represented in different channels. CNNs have achieved state-of-the-art performance for some computer vision tasks, such as image recognition. These networks are also known to mimic many properties of biological systems, such that each can be assigned a ``brain score''~\citep{schrimpf_brain-score_2020}. However, this score does not take into account key aspects of biological systems, such as inference speed or energy consumption. In particular, they do not take advantage of the dynamics inherent in the way we perceive our natural environment. In the vast majority of biological neural networks, on the other hand, information is represented as \emph{spikes}, prototypical all-or-nothing (binary) events whose only parameters are their timing and the address of the neuron that fired the spike~\citep{paugam-moisy_computing_2012}. Spiking neural networks (SNNs), known as the third generation of artificial neural networks, incorporate this temporal dimension into the way they perform their computations. They are of interest to computational neuroscience because they provide a better model of the biological neuron. One example of a SNN is the SpikeNet algorithm, which takes a purely temporal approach by encoding information using one spike per neuron~\citep{delorme_spikenet_1999}. Another type of SNN that uses the exact timing of spikes tries to determine the structure of the network to minimize a cost function, as implemented in the SpikeProp algorithm~\citep{bohte_error-backpropagation_2002}. This was recently extended using the surrogate gradient method which is now widely used in attempts to transfer the performance of CNNs to SNNs~\citep{zenke_remarkable_2021}. However, the performance of SNNs still lags behind that of networks using an analog, firing rate-based representation. The question of the advantage of using spikes in machine learning and computer vision remains open.
